\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-02-01 doc/USER_MANUAL/manual_SPECFEM3D.tex
re-adds TOPOGRAPHY flag to use with ocean load approximation; updates Makefiles; updates layered_halfspace example

>>>>

\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{OCEANS} is set to \texttt{.true.}.
Set to \texttt{.true.} if topography and
bathymetry should be read in based upon the topography file specified in the main
constants file \texttt{constants.h} found in subdirectory \texttt{src/shared/} to evaluate
elevations. If not set, elevations will be read from the numerical mesh.
